\begin{abstract}
Cluttered path clearing is not only about detecting blockages, but about deciding which width-constrained bottlenecks are worth intervening on and whether they can be opened through executable multi-robot interactions. Existing Navigation Among Movable Obstacles (NAMO) methods mainly reason about obstacle rearrangement at an abstract geometric level, while collaborative pushing methods focus on local contact execution without explicit guidance for multi-obstacle corridor construction. We present frontier gaps as a structured interface that connects these levels by converting reachable clearance bottlenecks into contact-feasible intervention queries. A W-clearance connectivity graph (WCCG) determines whether a traversable corridor already exists and, when it does not, exposes the reachable frontier gaps that currently block progress. For each selected gap, only gap-conditioned pushing candidates are generated for the adjacent movable obstacles, and short-horizon physical simulation is used to validate these induced interventions rather than to support generic downstream search. Building on this interface, a physics-informed hybrid search prioritizes and selectively expands only the most promising candidates. This formulation links bottleneck selection to executable contact generation, producing corridor-opening actions grounded in both scene geometry and physical feasibility. Simulation results and hardware experiments show that frontier-gap-guided planning improves path-clearing reliability while yielding action sequences that remain consistent with real multi-robot execution.
\end{abstract}