%==============================================
\subsection{WCCG-guided Gap Sequencing}\label{subsec:gap}

When the WCCG clearance certificate in~\eqref{eq:wccg_criterion} is not
satisfied, the planner must decide which narrow gap should be cleared first.
Passing all frontier gaps to the physics-informed hybrid search~(PIHS) would
create many unnecessary pushing tasks and simulation rollouts. Gap sequencing is
a lightweight WCCG-level lookahead that ranks frontier gaps before any contact
mode or physical rollout is generated.

\subsubsection{Search state and expansion}
A WCCG tracing query from a current source~$S_\ell$ toward the goal~$G$ either
reaches~$G$ or returns a frontier loop~$\Gamma_\ell$. The bridge--bridge edges
on~$\Gamma_\ell$ are candidate portal gaps. A sequencing node stores only a
partial gap sequence~$\mathbf{g}_{1:\ell}\triangleq(g_1,\cdots,g_\ell)$ and
the current tracing source~$S_\ell$; it does not include contact points, robot
motions, or object trajectories. Expanding a node selects one portal gap on the
current frontier loop, moves the tracing source to the opposite side of that
gap, and invokes the WCCG tracing query again. Nodes are expanded in a
best-first manner with a fixed beam width and maximum sequence length.

\subsubsection{Transition cost}
The cost of opening a portal gap is estimated by a recursive geometric
clearing computation. For each side of a gap, adjacent movable objects are
tested as possible clearing objects, and the estimate accounts for the required
opening displacement, object mass, friction, and recursively detected blockers
along the swept motion. This gives $\mathsf{C}_{\mathrm{gp}}(g,\mathbf{s})$ for
opening gap~$g$ at state~$\mathbf{s}$. When consecutive gaps can be improved by
compatible motions of the same movable object, their sequence cost is corrected
to avoid double-counting the same clearing action. Candidate gaps are expanded
in increasing order of this estimated clearing cost, with a weak goal-distance
tie breaker based on $\|\mathbf{p}_g-\mathbf{s}_{\texttt{V}}^{\texttt{G}}\|$,
where~$\mathbf{p}_g$ is the representative point of~$g$.

\subsubsection{Output and PIHS interface}
A completed sequencing node is one whose last WCCG tracing query reaches~$G$.
Let~$\mathfrak{G}(S,G)$ denote the completed sequences visited under the search
budget. The W-clearance cost-to-go estimate is
\begin{equation}\label{eq:state_c2g}
\widehat{\mathsf{J}}_{\mathrm{clr}}(\mathbf{s})\triangleq{}
\min_{\mathbf{g}\in\mathfrak{G}(S,G)}
\sum_{\ell=1}^{L}
\mathsf{C}_{\mathrm{gp}}(g_{\ell},\mathbf{s}_{\ell}),
\end{equation}
If the WCCG clearance
certificate in~\eqref{eq:wccg_criterion} already succeeds, then
$\widehat{\mathsf{J}}_{\mathrm{clr}}(\mathbf{s})=0$.
The resulting gap sequence is not a physical plan because it has not specified
contact modes or been validated by simulation. Only the first portal gap of the
best sequence is passed to the task sampler. PIHS then generates concrete
pushing candidates for this gap and validates them through contact-mode
generation and short-horizon physics rollout. The remaining gaps are
reconsidered after the accepted rollout updates the WCCG.

\begin{remark} 
Unlike path-first recursive clearing methods that commit to a geometric path 
and then remove obstacles from that path, 
the proposed planner first searches over WCCG-induced gap sequences. 
Each sequence represents a topological clearance alternative and is scored 
by the estimated difficulty of opening its blocking gaps. 
A lightweight reference polyline is derived only after a sequence is selected, 
and is used to bias local push-task generation rather than 
define a fixed corridor to be cleared. \hfill $\blacksquare$ 
\end{remark}