%==============================
\subsection{Overall Analyses}\label{subsec:overall}

\subsubsection{Execution and Online Adaptation}\label{subsec:execute}
The hybrid search returns a pushing schedule
$\pi = \{\tau_1,\cdots,\tau_K\}$, where
$\tau_k \triangleq (g_k,v_k,\boldsymbol{\xi}_k)$ specifies a target gap, a
short-horizon obstacle velocity, and a pushing mode. The schedule is executed
sequentially in a receding-horizon manner. For each $\tau_k$, the robots move
to the required contact configurations and apply the corresponding pushing
routine from the current state as in~\eqref{eq:sim}. During transition, robots
are reassigned by preserving the circular order of contact points along the
obstacle boundary~\cite{tang2024collaborative}, which reduces path crossings
under sufficient clearance. After each push, the system state is updated from
observation, and execution proceeds to $\tau_{k+1}$ if the action succeeds.
For consistency with execution, the WCCG is rebuilt periodically from
the current configuration. Execution terminates once a $W$--clear path
$\mathcal{P}^W_\texttt{V}$ connects $\mathbf{s}_t$ and
$\mathbf{s}_\texttt{V}^{\texttt{G}}$.
Replanning is triggered if nominal execution cannot continue reliably, e.g., if
reassignment is blocked by nearby obstacles; if the realized motion deviates
significantly from the simulated state, the current push fails; or if
the updated local geometry invalidates the remaining schedule. In such cases,
execution is aborted and Alg.~\ref{alg:push} is called from the updated state.


%----------------------------------------------
\subsubsection{Computational Complexity}\label{subsubsec:complexity}
Given~$M$ movable obstacles, let
$\mathcal{G}_W$ be the current WCCG in~\eqref{eq:wccg},
$\Gamma_{L_\nu}$ be the visible frontier-gap set at node~$\nu$,
and let~$\Xi_g$ be the candidate pushing-strategy set for gap~$g$.
Then one node expansion in Alg.~\ref{alg:push}
consists of:
(I) WCCG update and frontier extraction,
with complexity~$\mathcal{O}(M\log M + |\mathcal{V}| + |\mathcal{E}_c| + |\mathcal{E}_b|)$;
(II) gap ranking over~$\Gamma_{L_\nu}$,
with complexity~$\mathcal{O}(|\Gamma_{L_\nu}|\log |\Gamma_{L_\nu}|)$;
and
(III) candidate generation and validation over the ranked gaps. If
$C_{\mathrm{LP}}$ denotes the cost of one sparse LP in mode
generation,~$T_{\mathrm{sim}}$ the rollout horizon of one
$\mathsf{EvalSim}(\cdot)$ in~\eqref{eq:sim},~$n_{\texttt{w}}$ the number of parallel
simulations, and~$\rho_\nu\in[0,1]$ the fraction of validated candidates,
then the dominant complexity is
$\mathcal{O}(\sum_{g\in \mathsf{Rank}(\nu)} |\Xi_g|\, C_{\mathrm{LP}}
+\frac{\rho_\nu\, T_{\mathrm{sim}}}{n_{\texttt{w}}}
\sum_{g\in \mathsf{Rank}(\nu)} |\Xi_g|)$.
Hence, the overall cost per expansion is dominated by the
simulation process, while quick-pass, early stopping and parallel
rollouts can reduce the constant factors in practice.


%----------------------------------------------
\subsubsection{Generalization}\label{subsec:general}
The framework admits several extensions:
(I) \textit{Heterogeneous teams.} Per-robot gain tuning and robot-specific mode
priors enable cooperation among diverse robots;
(II) \textit{Concurrent pushing.} Multi-object mode generation and conflict-aware
transition planning allow multiple obstacles to be pushed simultaneously;
(III) \textit{Dynamic environments.} Periodic $W$--connectivity checks and
on-demand replanning handle disturbances such as object drift or unmodeled
contacts during execution.
