%==============================================
\subsection{W--Clearance Connectivity Graph}\label{subsec:wccg}

The feasibility of routing the vehicle reduces to whether a~$W$-width corridor
connects~$\mathbf{x}_\texttt{V}^{\texttt{S}}$ and~$\mathbf{x}_\texttt{V}^{\texttt{G}}$.
A W--clearance connectivity graph (WCCG) is introduced in this work as shown in Fig.~\ref{fig:wccg},
which encodes obstacle adjacencies under clearance~$W$ and enables \emph{fast connectivity queries}.
Constructed directly from geometry  rather than grids or roadmaps,
it avoids discretization error and remains consistent—crucial because connectivity is checked repeatedly
during planning.

\subsubsection{Graph Construction}
The WCCG is built by decomposing all clearance-relevant obstacle and workspace
boundaries into convex components or segments.
From each component
$C$, a centroid node~$v_c$ is created. When two components~$C_u$ and~$C_v$
have closest points~$p_u\in C_u$ and~$p_v\in C_v$ with distance less than~$W$,
bridge nodes are added at~$p_u$ and~$p_v$. These bridge nodes are
connected by a bridge--bridge edge, annotated with the gap width
$w_{uv}\triangleq\|p_u-p_v\|$, and further linked back to their centroids with
centroid--bridge edges. Narrow passages with~$w_{uv}<W$ are marked
as potential bottlenecks. The resulting graph is given by:
\begin{equation}\label{eq:wccg}
\mathcal{G}_W\triangleq(\mathcal{V},\; \mathcal{E}_c\cup\mathcal{E}_b),
\end{equation}
where~$\mathcal{V}$ contains all centroid and bridge nodes;
$\mathcal{E}_c$ is the set of centroid--bridge edges; and~$\mathcal{E}_b$ the
set of bridge--bridge edges annotated by widths~$w_{uv}$.

\subsubsection{Connectivity Criterion}\label{subsubsec:bugplanner}
Once~$\mathcal{G}_W$ has been constructed, connectivity queries can be
performed without explicitly computing a geometric path. A frontier-tracing
procedure, similar to the BugPlanner~\cite{McGuireCroonTuyls2019}, starts from the vehicle start
$\mathbf{x}_\texttt{V}^{\texttt{S}}$, casts a ray toward the goal
$\mathbf{x}_\texttt{V}^{\texttt{G}}$, and explores the encountered loop of
frontier edges. If a valid exit is discovered, the process continues until the
goal is reached; otherwise a blocking cycle is returned. Successful execution
produces a skeleton~$\Sigma$, as an ordered sequence of centroid and
bridge nodes that certifies~$\mathbf{x}_\texttt{V}^{\texttt{S}}$ and
$\mathbf{x}_\texttt{V}^{\texttt{G}}$ lie in the same connected face.
Using the admissible reference-center space~$\mathcal{F}_W(t)$ defined in
Section~\ref{subsec:vehicle}, the WCCG connectivity criterion for
\eqref{eq:wclear} is
\begin{equation}\label{eq:wccg_criterion}
  \big{(}\mathbf{x}_\texttt{V}^{\texttt{S}},\, \mathbf{x}_\texttt{V}^{\texttt{G}}
  \; \text{belong to the same face of}\; \mathcal{G}_W\big{)},
\end{equation}
and $\mathbb{B}_{W/2}(\mathbf{x}_\texttt{V}^{\texttt{S}}),\,
\mathbb{B}_{W/2}(\mathbf{x}_\texttt{V}^{\texttt{G}})\subset\mathcal{F}_W$.
This aligns with~\eqref{eq:wclear} for clearance.


% \subsubsection{Frontier-Gap Interface}
% If the connectivity criterion fails, the frontier-tracing procedure returns a
% blocking cycle~$\mathcal{L}$ instead of a skeleton. The bridge--bridge edges on
% $\mathcal{L}$ expose the frontier gaps whose widths are insufficient for the
% vehicle. These gaps form the interface between WCCG connectivity reasoning and
% the gap-ranking module described next.

\begin{remark}\label{remark:wccg}
Unlike sampling or grid-based planners, the WCCG avoids workspace
discretization and thus eliminates resolution-induced errors. Its purely
geometric construction also enables efficient connectivity and clearance
queries, which are repeatedly invoked by the hybrid planner below.
\hfill$\blacksquare$
\end{remark}





%% \begin{algorithm}[t!]
%% \small
%% \caption{BugPlanner for~$W$-width connectivity (skeleton witness)}
%% \label{alg:bugplanner}
%% \DontPrintSemicolon
%% \SetKwInOut{Input}{In}\SetKwInOut{Output}{Out}
%% \Input{$\mathbf{s}^{\texttt{S}}$,~$\mathbf{s}^{\texttt{G}}$, WCCG}
%% \Output{if connected: skeleton~$\Sigma$; else: frontier loop~$\mathcal{L}$}
%%~$P\leftarrow\mathbf{s}^{\texttt{S}}$,~$\Sigma\leftarrow[\ ]$\;
%% \While{true}{
%%   \If{segment~$P\mathbf{s}^{\texttt{G}}$ hits no edge}{\Return~$\Sigma \cup \{\texttt{straight}(P,\mathbf{s}^{\texttt{G}})\}$}
%%   Build loop~$\mathcal{L}$ by angle-follow from the hit edge; append traversed edges to~$\Sigma$\;
%%   \If{$\mathrm{parity}(\mathcal{L},\,\mathbf{s}^{\texttt{S}}\mathbf{s}^{\texttt{G}})$ is odd}{\Return~$(\emptyset,\mathcal{L})$}
%%   Choose exit~$e$ on~$\mathcal{L}$ (outward normal~$\to\,\mathbf{s}^{\texttt{G}}$); append arc to~$\Sigma$;~$P\leftarrow e$ (tiny bias)\;
%% }
%% \end{algorithm}
